### 2016-09-06 FrontBackmatter/Introduction.tex
Adjust TOC bookmarks

\chapter*{Introduction}
\pdfbookmark[1]{Introduction}{introduction}

@@

Chemistry can be largely considered a \emph{wet} science: almost always
chemical phenomena happen in a liquid environment.~\autocite{Reichardt2010-le}
We hereby define a "solution", or more generally an "environment", as
a system were the number of solvent molecules exceeds by far the number
of solute molecules.~\autocite{Tomasi2004-dc, Tomasi2007-es}
It is then clear that theoretical and computational approaches to such a
problem will necessarily suffer from a \emph{dimensionality disease}.
The number of degrees of freedom to be taken into account is, in
principle, so large, that even the most advanced computing machines
would have a hard time computing the desired observables.
Moreover, on an interpretive level, it would not even be desirable to
have such a detailed insight.
As is well known from statistical mechanics, microscopic detail cannot
account for the macroscopic behaviour.~\autocite{Hill1960-ql,
Hansen2013-io}
To tame this complexity and cure the disease, one must devise
\emph{models} that simplify physical reality, while offering tools for
understanding reality and predicting new and exciting
phenomena.~\autocite{Anderson1972-ai, Winsberg2010-sy, Kovac2011-ew}
One of the earlier attempts at tackling the problem of solvation is due
to \citeauthor{Onsager1936-wf}. His was a rather crude model, but one
that has had a lasting impact and informs much of the developments that
will be presented in this thesis.~\autocite{Onsager1936-wf}

Before introducing our model of choice, let us consider how an
environment might affect molecular observables of interest.
Environment effects are usually classified as:
\begin{description}[font=\normalfont\scshape]
\item[Direct.]
  These effect stem straightforwardly from the modification underwent by
  the solute electronic density when interacting with the environment.
\item[Indirect.]
  It is common for solutes to exhibit different minimum-energy
  conformations in different environments. These effects are commonly
  labelled as indirect.
\item[Local field.]
  Light-matter interactions are also affected by the environment. Local
  modifications of externally applied fields subtly influence molecular
  responses.~\autocite{Cammi1998-jp, Pipolo2014-sd}
\item[Dynamic.]
  Probing the nature of molecular excited states has enormous
  technological impact. The presence of the environment radically
  influences excited states, since relaxation processes in the medium
  become important.
\item[Specific.] This catch-all category includes all effects
  stemming from the peculiar solute-solvent pair interactions that
  cannot be fully described under any of the previous labels.
  In general, modelling such effects demands an atomistic level of
  detail.
\end{description}

Faced with the problem of describing such a diverse array of effects,
two main models have emerged in the past decades, each with its
strengths and weaknesses.
Both can be classified as \emph{multiscale} (or \emph{focused})
models~\autocite{Nobel2013} and hinge on the same idea: treat different
parts of the system with different methods and couple these methods by
bridging "scales" at the boundary, \emph{vide infra}.
While both models treat the molecular degrees of freedom at the quantum
mechanical level, their approach to the microscopic description of the
degrees of freedom of the environment differs:
\begin{itemize}
 \item
   \emph{Discrete} (or \emph{explicit}) models explicitly treat those
   degrees of freedom.
   This is either achieved by a cheaper quantum mechanical
   method~\autocite{Vreven2006-gx} or by \gls{MM}.~\autocite{Senn2009-sk}
   In the latter approach, commonly dubbed \acrshort{QM}/\acrshort{MM}, the \acrshort{MM}
   region can either be polarizable~\autocite{Mennucci2013-go,
   Olsen2010-wa, Lipparini2011-rd} or non
   polarizable. While the former method allows for mutual polarization
   between the \acrshort*{QM} and \acrshort*{MM} subsystems, the latter
   treats the \acrshort*{MM} region as fixed.
 \item
   \emph{Continuum} (or \emph{implicit}) completely remove the degrees
   of freedom of the environment from the picture, replacing it with a
   structureless continuum.
   The effect of this continuum is described, classically, \emph{via}
   its bulk properties.~\autocite{Onsager1936-wf, Miertus1981-mm}
\end{itemize}
\acrshort{QM}/\acrshort{MM} models can capture, albeit approximately, the effect
of the atomistic nature of the environment on the active part of the
system.
However, they demand a statistical average of environment configurations
to yield results of any significance. Moreover, a large number
\emph{cutoff} for the \acrshort{MM} region is usually required to converge
long-range electrostatic interactions.\autocite{Steindal2011-ki}
Continuum models avoid both problems at once. Statistical averaging is
built into the model \emph{via} their parametrization by
means of the environment's bulk properties, such as the permittivity.
In addition, long-range electrostatics is treated exactly.
Unfortunately, atomistic detail is lost and it is then impossible to
recover a satisfactory description of specific effects.
To partly alleviate these sources of error, the
\acrshort{QM}/\acrshort{MM} and \acrshort{QM}/Continuum methods can and
have been successfully combined to yield the three-layer
\acrshort{QM}/\acrshort{MM}/Continuum method.\autocite{Steindal2011-ki,
Lipparini2011-rd, Caprasecca2012-ir, Lipparini2013-ud}
Figure \ref{fig:qm-to-multiscale} schematically portrays the transition
from a full \acrshort{QM} model of the relevant system to its multiscale
representations.

@@

>>>>

\chapter*{Introduction}
\refstepcounter{dummy}
\phantomsection
\addcontentsline{toc}{chapter}{\tocEntry{Introduction}}

@@

Chemistry can be largely considered a \emph{wet} science: almost always
chemical phenomena happen in a liquid environment.~\autocite{Reichardt2010-le}
We hereby define a "solution", or more generally an "environment", as
a system where the number of solvent molecules exceeds by far the number
of solute molecules.~\autocite{Tomasi2004-dc, Tomasi2007-es}
It is then clear that theoretical and computational approaches to such a
problem will necessarily suffer from a \emph{dimensionality disease}.
The number of degrees of freedom to be taken into account is, in
principle, so large, that even the most advanced computing machines
would have a hard time computing the desired observables.
Moreover, on an interpretive level, it would not even be desirable to
have such a detailed insight.
As is well known from statistical mechanics, microscopic detail cannot
account for the macroscopic behaviour.~\autocite{Hill1960-ql,
Hansen2013-io}
To tame this complexity and cure the disease, one must devise
\emph{models} that simplify physical reality, while offering tools for
understanding reality and predicting new and exciting
phenomena and properties.~\autocite{Anderson1972-ai, Winsberg2010-sy, Kovac2011-ew}
One of the earlier attempts at tackling the problem of solvation is due
to \citeauthor{Onsager1936-wf}. His was a rather crude model, but one
that has had a lasting impact and informs much of the developments that
will be presented in this thesis.~\autocite{Onsager1936-wf}

Before introducing our model of choice, let us consider how an
environment might affect molecular observables of interest.
Environment effects are usually classified as:
\begin{description}[font=\normalfont\scshape]
\item[Direct.]
  These effects stem straightforwardly from the modification underwent by
  the solute electronic density when interacting with the environment.
\item[Indirect.]
  It is common for solutes to exhibit different minimum-energy
  conformations in different environments. These effects are commonly
  labelled as indirect.
\item[Local field.]
  Light-matter interactions are also affected by the environment. Local
  modifications of externally applied fields subtly influence molecular
  responses.~\autocite{Cammi1998-jp, Pipolo2014-sd}
\item[Dynamic.]
  Probing the nature of molecular excited states has enormous
  technological impact. The presence of the environment radically
  influences excited states, since relaxation processes in the medium
  become important.
\item[Specific.] This catch-all category includes all effects
  stemming from the peculiar solute-solvent pair interactions that
  cannot be fully described under any of the previous labels.
  In general, modelling such effects demands an atomistic level of
  detail.
\end{description}

Faced with the problem of describing such a diverse array of effects,
two main models have emerged in the past decades, each with its
strengths and weaknesses.
Both can be classified as \emph{multiscale} (or \emph{focused})
models~\autocite{Nobel2013} and hinge on the same idea: treat different
parts of the system with different methods and couple these methods by
bridging "scales" at the boundary.
Figure \ref{fig:qm-to-multiscale} schematically portrays the transition
from a full \acrshort{QM} model of the relevant system to its multiscale
representations.

@@

While both models treat the molecular degrees of freedom at the quantum
mechanical level, their approach to the microscopic description of the
degrees of freedom of the environment differs:
\begin{itemize}
 \item
   \emph{Discrete} (or \emph{explicit}) models explicitly treat those
   degrees of freedom.
   This is either achieved by a cheaper quantum mechanical
   method~\autocite{Vreven2006-gx} or by \gls{MM}.~\autocite{Senn2009-sk}
   In the latter approach, commonly dubbed \acrshort{QM}/\acrshort{MM}, the \acrshort{MM}
   region can either be polarizable~\autocite{Mennucci2013-go,
   Olsen2010-wa, Lipparini2011-rd} or non
   polarizable. While the former method allows for mutual polarization
   between the \acrshort*{QM} and \acrshort*{MM} subsystems, the latter
   treats the \acrshort*{MM} region as fixed.
 \item
   \emph{Continuum} (or \emph{implicit}) completely remove the degrees
   of freedom of the environment from the model, replacing them with a
   structureless continuum.
   The effect of this continuum is described, classically, \emph{via}
   its bulk properties.~\autocite{Onsager1936-wf, Miertus1981-mm}
\end{itemize}

\acrshort{QM}/\acrshort{MM} models can capture, albeit approximately, the effect
of the atomistic nature of the environment on the active part of the
system.
However, they demand a statistical average of environment configurations
to yield results of any significance. Moreover, a rather large
\emph{cutoff radius} for the \acrshort{MM} region is usually required to converge
long-range electrostatic interactions.\autocite{Steindal2011-ki}
Continuum models avoid both problems at once. Statistical averaging is
built into the model \emph{via} their parametrization by
means of the environment's bulk properties, such as the permittivity.
In addition, long-range electrostatics is treated exactly.
Unfortunately, atomistic detail is lost and it is then impossible to
recover a satisfactory description of specific effects.
To partly alleviate these sources of error, the
\acrshort{QM}/\acrshort{MM} and \acrshort{QM}/Continuum methods can and
have been successfully combined to yield the three-layer
\acrshort{QM}/\acrshort{MM}/Continuum method.\autocite{Steindal2011-ki,
Lipparini2011-rd, Caprasecca2012-ir, Lipparini2013-ud}
